Why Real-World Subgraph Isomorphism is Easy, \\ and What This Means for Graph Databases

### 2016-10-23 paper/paper.tex
Please Sir, can I have some more?

The filter / verify paradigm also influences other research. For example, recently
\citet{DBLP:journals/pvldb/YuanMG13} continue a line of supergraph search work, again using a
filtering step to avoid subgraph isomorphism calls.  \citet{DBLP:journals/tkde/HongZLY15} look at
graph database subgraph matching with an additional set similarity constraint, and state that
Ullmann's algorithm and VF2 are ``usually costly for large graphs'' because they ``do not utilize
any index structure''. They propose an indexing structure, which takes over 2,000 seconds to
construct, and uses nearly 2GBytes of space.  There is also research into maintaining indices when
the set of target graph changes: for example \citet{DBLP:conf/sigmod/YuanMYG15} look at algorithms
for updating graph indices. And in describing a system for reusing results of queries which are sub-
or super-graphs of previous queries, \citet{DBLP:conf/edbt/WangNT16} state that querying is a ``very
costly operation as it entails the \NP-complete problem of subgraph isomorphism'', and place ``an
emphasis on the number of unnecessary subgraph isomorphism tests''.

>>>>

The filter / verify paradigm also influences other research. For example, it is used by
\citet{DBLP:conf/icde/TianP08} in an approximate subgraph searching system: they state that
Ullmann's algorithm ``is prohibitively expensive for querying against [a] database with a large
number of graphs'', and that indices are used ``to filter out graphs that do not match the query''.
More recently, \citet{DBLP:journals/pvldb/YuanMG13} continue a line of supergraph search work, again
using a filtering step to avoid subgraph isomorphism calls (in the opposite direction, so queries
are now target graphs). \citet{DBLP:journals/tkde/HongZLY15} look at graph database subgraph
matching with an additional set similarity constraint, and state that Ullmann's algorithm and VF2
are ``usually costly for large graphs'' because they ``do not utilize any index structure''. They
propose an indexing structure, which takes over 2,000 seconds to construct, and uses nearly 2GBytes
of space.  There is also research into maintaining indices when the set of target graph changes: for
example \citet{DBLP:conf/sigmod/YuanMYG15} look at algorithms for updating graph indices. And in
describing a system for reusing results of queries which are sub- or super-graphs of previous
queries, \citet{DBLP:conf/edbt/WangNT16} state that querying is a ``very costly operation as it
entails the \NP-complete problem of subgraph isomorphism'', and place ``an emphasis on the number of
unnecessary subgraph isomorphism tests''.
